The Astropy Project: Building an inclusive, open science project and status of the v2.0 software

### 2018-01-08 main.tex
Added brief description of HDF5 I/O

>>>>

\subsubsection{HDF5}

The \package{astropy.io.misc.hdf5} subpackage provides support for binary
read and write access to files in the \emph{Hierarchical Data Format}
(HDF5), if the \package{h5py} package is installed. Astropy table I/O
is offered transparently through \texttt{Table.read()} and
\texttt{Table.write()}, analogously to the other auto-detected
formats. The keyword \texttt{path='group/subgroup/dataset'} specifies
the path to the data inside the file's hierarchical structure.
